---
title: "Interactive Safety Reports for DMC"
output:
  flexdashboard::flex_dashboard:
    theme: 
      version: 4
      fg: "#00857C"
      bg: "#FFFFFF"
---

<style>
/* Set font color of inactive tab to green */
.nav-tabs-custom .nav-tabs > li > a {
  background-color: #00857C;
  color: #FFFFFF;
} 

/* Set font color of active tab to red */
.nav-tabs-custom .nav-tabs > li.active > a {
  background-color: #00857C;
  color: #FFFFFF;
} 

/* To set color on hover */
.nav-tabs-custom .nav-tabs > li.active > a:hover {
  background-color: #00857C;
  color: #FFFFFF;
}
</style>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE, 
  warning = FALSE
)
```

```{r setup}
library(flexdashboard)
library(reactable)
library(downloadthis)
```

Sidebar {.sidebar}
=======================================================================

### MK9999

```{r}
download_file("dmc_report.Rmd", button_label = "Download Reports")
```

Cutoff date: 2021-10-19

Study Information
=======================================================================

Demographic
=======================================================================

Adverse Events
=======================================================================

Row {.tabset .tabset-fade}
-------------------------------------

### AE Summary 

```{r}
reactable(iris[1:5,])
```

### Specific AE

```{r}
shiny::selectInput(inputId = "ae_filter", 
                   label = "\n\nAE Filter", 
                   choices = c("Any AE", "Drug-related AE"))
```


```{r}
reactable(iris[6:10, ])
```

### AE of Special Interest 

```{r}
reactable(iris[11:15,])
```

Labs
=======================================================================

Exposure
=======================================================================

