---
title: "Interactive Forest Plot for DMC"
output:
  html_document:
    self_contained: no
    number_sections: yes
    code_folding: hide
  pdf_document: default
vignette: |
  %\VignetteIndexEntry{Interactive Forest Plot for DMC} %\VignetteEngine{knitr::rmarkdown} %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE, 
  warning = FALSE
)
```


This vignette introduces the construction of an interactive forest plot for the review of the Data Monitoring Committee (DMC).
The interactive features include:

- Labels can be revealed by hovering the mouse over a point.
- Details can be listed by clicking $\blacktriangledown$.
- Search bars are embedded for users to find the targeted adverse events (AE).
- AE tables can be downloaded as .rft files.
- Filters can be applied, i.e., filter the 

  - discontinued due to an adverse event;
  - with drug-related adverse events;
  - with serious adverse events;
  - with toxicity grade 3-5 adverse events.
  
The procedures to generate a forest plot with the above interactive features are listed as follows.

- Step 0: Get standardized _adsl_ and _adae_ tables. 
- Step 1: Use `tidy_ae_table2()` function (developed in this package) to get a tidy AE table.
- Step 2: Use `download_ae()` function (developed in this package) to generate a download button If you click this download button, you will download a .zip file, which consists AE summary table with custom filters, for example, serious AE, drug-related AE, etc.
- Step 3: Use `plot_forest()` function (developed in this package) to generate an interactive forest plot. 

# Load Required Packages 
```{r setup}
library(DescTools)      # Compare risk difference (Obtain confidence interval)
library(plotly)         # Interactive figure 
library(reactable)      # Interactive table 
library(dplyr)          
library(tidyr)
library(crosstalk)
library(crosstool)      # A generic control widget for crosstalk.        
library(htmltools)
library(downloadthis)   # To implement download buttons in HTML output from RMarkdown
library(r2rtf)          # Generate rtf for download
devtools::load_all()
```


# Data Preparation

## Impute Data
Because there are some variables missing in the example data set, we first impute the data set. 

- Impute `adae$ATOXGR`: if `adae$AESDTH='Y'` then `adae$ATOXGR='5'`, and random assign toxicity grade for other AE records;
- Generate `Grade3To5Flag` from `adae$ATOXGR`: `Grade3To5Flag` = "Y" if `adae$ATOXGR`>=3, otherwise `Grade3To5Flag` = "N". [create check box for 1,2,3,4,5? (Difficult to implement now, maybe left for future work).
- Impute `adae$AEACN`: `adae$AEACN` = `"DOSE NOT CHANGED"` or `"DRUG INTERRUPTED"` or `"DRUG WITHDRAWN"`. Here we impute 5% who discontinue drug (`DRUG WITHDRAWN`) and select the latest AE as `"DRUG WITHDRAWN"`.

```{r}
## Impute `adae$ATOXGR`
temp_fun <- function(x) {
    
  if(x == "Y"){
    return("5")
    }else{
    return(as.character(sample(1:4, size = 1, replace = TRUE)))
  }
}
adae <- adae %>% mutate(ATOXGR = unlist(adae$AESDTH %>% purrr:::map(temp_fun)))

## Generate `Grade3To5Flag`
adae <- adae %>% mutate(Grade3To5Flag = ifelse(ATOXGR %in% c("3", "4", "5"), "Y", "N"))

## Impute `adae$AEACN`
adae$AEACN = sample(c("DOSE NOT CHANGED", "DRUG INTERRUPTED", "DRUG WITHDRAWN"), 
                    size = length(adae$AEACN), prob = c(0.7, 0.25, 0.05), replace = TRUE)

## Impute stratum 
adsl$STRATUMN <- sample(seq(1,3), size = length(adsl$USUBJID), prob = c(0.3, 0.3, 0.4), replace = TRUE)

adae <- adae %>% left_join(data.frame(USUBJID = adsl$USUBJID, STRATUMN = adsl$STRATUMN))
```



## Define Analysis Data
```{r}
# tidy_ae_table is defined in R/ folder with same name 
# obtain AE information ready for visualization

db <- tidy_ae_table(population_from  = adsl %>% rename(TRTA = TRT01A),
                    observation_from = adae,
                    population_where = NULL,
                    observation_where = NULL,
                    treatment_var = "TRTA",
                    treatment_order = c("MK9999" = "Xanomeline High Dose", "Placebo" = "Placebo"),
                    stratum_var = "STRATUMN", #if there is not stratum, then stratum_var = NULL
                    #stratum_var = NULL,
                    ae_var = "AEDECOD",
                    ae_interested = define_ae_select_list(ae_criterion = c('AESER == "Y"', 'AEREL != "NONE"',
                                                                           'Grade3To5Flag == "Y"', 
                                                                           'AEACN == "DRUG WITHDRAWN"'),
                                                          ae_label = c("with serious adverse events",
                                                                       "with drug-related adverse events",
                                                                       "with toxicity grade 3-5 adverse events",
                                                                       "discontinued due to an adverse event")),
                    listing_interested = define_ae_listing(listing_var = c("SITEID", "USUBJID", "SEX", "RACE", "AGE",  
                                                                           "AETERM", "TRTA", "ADURN", "ADURU",
                                                                           "AESEV",  "AESER", "AEREL", "AEACN", "AEOUT"),
                                                           listing_label = c("Site Number", "Participant ID", "Gender", "Race", "Age",
                                                                             "AE", "Onset Epoch", "Duration", "Duration", 
                                                                             "Intensity", "Serious", "Related", "Action Taken",
                                                                             "Outcome"))
                    )
```

# Download the AE Summary Count Table

```{r}
temp_dir <- tempdir()
ae_summary <- tlf_ae_summary(population_from = adsl %>% rename(TRTA = TRT01A),
                             observation_from = adae,
                             population_where = "ITTFL=='Y'",
                             observation_where = NULL,
                             treatment_var = "TRTA",
                             treatment_order = c("MK9999" = "Xanomeline High Dose", "Placebo" = "Placebo"),
                             ae_var = "AEDECOD",
                             ae_interested = define_ae_select_list(ae_criterion = c('AESER == "Y"', 
                                                                                    'AEREL != "NONE"',
                                                                                    'Grade3To5Flag == "Y"',
                                                                                    'AEACN == "DRUG WITHDRAWN"'),

                                                                   ae_label = c("with serious adverse events",
                                                                                "with drug-related adverse events",
                                                                                "with toxicity grade 3-5 adverse events",
                                                                                "discontinued due to an adverse event")),
                             #stratum_var = "STRATUMN", 
                             stratum_var = NULL,
                             display_ci = TRUE,
                             display_total = FALSE,
                             title_text = "Analysis of Adverse Event Summary",
                             subtitle_text = NULL,
                             end_notes = "Every subject is counted a single time for each applicable row and column.",
                             output_report = file.path(temp_dir, 'ae0summary.rtf'),
                             output_dataframe = file.path(temp_dir, 'ae0summary.RData'))

ae_spec <- tlf_ae_specific(population_from = adsl %>% rename(TRTA=TRT01A),
                           observation_from = adae,
                           population_where = "ITTFL == 'Y'",
                           observation_where = NULL,
                           treatment_var = "TRTA",
                           treatment_order = c("MK9999" = "Xanomeline High Dose", "Placebo" = "Placebo"),
                           ae_var = "AEDECOD",
                           ae_grp = "AEBODSYS",
                           stratum_var = "STRATUMN", #stratum_var = NULL,
                           display_ci = FALSE,
                           display_total = FALSE,
                           display_pval = FALSE,
                           title_text = "Participants With Adverse Events by System Organ Class and Preferred Term",
                           subtitle_text = c("(Incidence > 0% in More or More Treatment Group)","(APaT Population)"),
                           end_notes = "Every subject is counted a single time for each applicable row and column.
Database Cutoff Date: 01SEP2021.",
                           output_report = file.path(temp_dir, 's01specific0ae0soc.rtf'),
                           output_dataframe = file.path(temp_dir, 'ae0spec.RData'))

tlf_download(temp_dir)
```


# Construct Interactive Forest Plot

```{r}
forestly(db, 
         fig_prop_color = c("#00857C", "#66203A"),
         fig_prop_label = NULL, # c("Treatment", "Placebo"), 
         fig_diff_color = "black", 
         fig_diff_label = NULL, # "Treatment <- Favor -> Placebo",
         small_sample = c(4, 4)) 
```






