---
title: "onboarding"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Datasets: 

`adsl`: subject level information
`adae`: adverse events information one record per row. 

Source: https://bitbucket.cdisc.org/projects/CED/repos/sdtm-adam-pilot-project/browse/updated-pilot-submission-package/900172/m5/datasets/cdiscpilot01/analysis/adam/datasets

```{r}
devtools::load_all()        # https://r-pkgs.org/whole-game.html
head(adsl)[,1:5]            # dataset saved in the data folder will be loaded 
```


> You are able to see dataest label by using `View(adsl)`. More details can be found in the [data guide](https://bitbucket.cdisc.org/projects/CED/repos/sdtm-adam-pilot-project/browse/updated-pilot-submission-package/900172/m5/datasets/cdiscpilot01/analysis/adam/datasets/dataguide.pdf)

## Adverse Events Structure

- Adverse Events (AE) term: `adae$AEDECOD`
- Source of Organ (SOC) `adae$AESOC`
- Serious AE `adae$AESER`
- Drug related AE `adae$AEREL`
- AE result in death `adae$AEOUT`

Note: Each AE term belongs to an SOC. 

As a clinician, I would be interested to explore the adverse events in multiple layers. 

1. How many (N and %) subjects encounter AE? (by AE term and by SOC)
2. How many (N and %) subjects encounter serious AE? (by AE term and by SOC)
3. How many (N and %) subjects encounter drug related AE? (by AE term and by SOC)
4. How many (N and %) subjects encounter drug related serious AE? (by AE term and by SOC)
5. How many (N and %) subjects encounter drug related AE result in death? (by AE term and by SOC)
6. For AE of particular interest, who are they? 

## Demo

Refer `vignettes/example.Rmd` or the compiled one at 


