---
title: 'Miettinen and Nurminen method without or with stratification'
author: "Xuan Deng"
date: '`r Sys.Date()`'
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: yes
  flexdashboard::flex_dashboard:
    vertical_layout: fill
  html_notebook:
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: yes
---

# Summary

Binary outcome is commonly used endpoint in clinical trials. This page is to illustrate how to conduct the unstratified or stratified analysis with Miettinen and Nurminen method (M&N) for risk difference analysis R. The following statistics can be calculated within the function: estimated risk difference, confidence interval for the difference, p-value for risk difference with a delta that specified. 

# Reference

Miettinen, O. and Nurminen, M, \emph{Comparative Analysis of Two Rates}. STATISTICS IN MEDICINE, 4:213-226, 1985.

# Statistical Methods
## MN method for unstratified analysis
Assume the data includes two independent binomial samples with binary response variables to be
analyzed/summarized and the data collected in a clinical design without stratification. Also this
approach is applicable to the case when the data are collected using a stratified clinical design and
the statistician would like to ignore stratification by pooling the data over strata assuming two
independent binomial samples. Assume $P_i$ is the proportion of success responses in the test ($i=1$) or control ($i=0$) group.  

### *Confidence Interval*  
The confidence interval is based on by M&N method and given by the roots for $PD=P_1-P_0$ of the equation:  
$$\chi_\alpha^2 = \frac{(\hat{p}_1-\hat{p}_0-PD)^2}{\tilde{V}}$$,  
where $\hat{p}_1$ and $\hat{p}_0$ are the observed values of $P_1$ and $P_0$, respectively;  
$\chi_\alpha^2$ = the upper cut point of size $\alpha$ from the cnetral chi-square distribution with 1 degree of freedom ($\chi_\alpha^2 = 3.84$ for $95$% confidence interval);  
$PD$ = the difference between two population proportions ($PD=P_1-P_0$);  
$$\tilde{V}=[\frac{\tilde{p}_1(1-\tilde{p}_1)}{n_1}+\frac{\tilde{p}_0(1-\tilde{p}_0)}{n_0}]\frac{n_1+n_0}{n_1+n_0-1}$$;  
$n_1$ and $n_0$ are the sample sizes for the test and control group, respectively;  
$\tilde{p}_1$ = maximum likelihood estimate of proprotion on test computed as $\tilde{p}_0+PD$;  
$\tilde{p}_0$ = maximum likelihood estimate of proprotion on control under the constraint $\tilde{p}_1-\tilde{p}_0=PD$.  

As stated above the 2-sided $100(1-\alpha)$% CI is given by the roots for $PD=P_1-P_0$. The bisection algorithm is used in the function to obtain the two roots (confidence interval) for $PD$.

### *P-value and Z-statistic*  
The Z-statistic is computed as:  
$$Z_{diff}=\frac{\hat{p}_1-\hat{p}_0+S_0}{\sqrt{\tilde{V}}}$$
where $\hat{p}_1$ and $\hat{p}_0$ are the observed values for $P_1$ and $P_0$ respectively, $S_0$ is pre-specified proprotion difference under the null;  
$\tilde{p}_1$ = maximum likelihood estimate of proprotion on test computed as $\tilde{p}_0+S_0$;  
$\tilde{p}_0$ = maximum likelihood estimate of proprotion on control under the constraint $\tilde{p}_1-\tilde{p}_0=S_0$.  

* For non-inferiority or one-sided equivalence hypothesis with $S_0>0$, the p-value, $Pr(Z\ge Z_{diff}|H_0)$, is computed based on $Z_{diff}$ using the standard normal distribution. 
* For non-inferiority or one-sided equivalence hypothesis with $S_0<0$, the p-value, $Pr(Z\le Z_{diff}|H_0)$, is computed based on $Z_{diff}$ using the standard normal distribution. 
* For two-sided supriority test, the p-value $Pr(\chi_{diff}^2\le \chi_1^2|H_0)$, is computed based on $\chi_{diff}^2$ using the chi-square distribution with 1 degree of freedom, where $\chi_{diff}^2=Z_{diff}^2$.

## MN method for stratified analysis
Assume the data includes two treatment groups, test and control, and collected based on a stratified design. Within each stratum there are two independent binomial samples with binary response variables to be analyzed/summarized. The parameter of interest is the difference between the population proportions of the test and the control groups. The analysis and summaries need to be performed while adjusting for the stratifying variables.  


### *Confidence Interval*  
The confidence interval is based on by M&N method and given by the roots for $PD=P_1-P_0$ of the equation:  
$$\chi_\alpha^2 = \frac{(\hat{p}_1^*-\hat{p}_0^*-PD)^2}{\sum_{i=1}^I(W_i/\sum_{k=1}^{K}W_k)^2\tilde{V}_i}$$,  
where $\hat{p}_s^* = \sum_{i=1}^I(W_i/\sum_{k=1}^KW_k)\hat{p}_{si}$ for $s=0,1$;  
$$\tilde{V}_i=[\frac{\tilde{p}_{1i}(1-\tilde{p}_{1i})}{n_{1i}}+\frac{\tilde{p}_{0i}(1-\tilde{p}_{0i})}{n_{0i}}]\frac{n_{1i}+n_{0i}}{n_{1i}+n_{0i}-1}$$;  
$W_i$ is the weight for the $i^{th}$ strata;  
$I = K = $ number of strata, $i=k=$ strata;  
$n_{1i}$ and $n_{0i}$ are the sample sizes in $i^{th}$ strata for the test and control group, respectively;  
$\hat{p}_{1i}$ and $\hat{p}_{0i}$ = observed proportion in $i^{th}$ strata for the test and control, respectively;  
$\tilde{p}_{0i}$ and $\tilde{p}_{1i}$ are MLE for $P_{0i}$ and $P_{1i}$, respectively, computed under the constraint $\tilde{p}_{1i}=\tilde{p}_{0i}+PD$.  

Similarly as for unstratified analysis,the 2-sided $100(1-\alpha)$% CI is given by the roots for $PD=P_1-P_0$, and the bisection algorithm is used in the function to obtain the two roots (confidence interval) for $PD$.

### *P-value and Z-statistic*  
The Z-statistic is computed as:  
$$Z_{diff}=\frac{\hat{p}_1^*-\hat{p}^*_0+S_0}{\sqrt{\sum_{i=1}^I(W_i/\sum_{k=1}^{K}W_k)^2\tilde{V}_i}}$$
where $S_0$ is pre-specified proprotion difference under the null;  
$\tilde{p}_{0i}$ and $\tilde{p}_{1i}$ are MLE for $P_{0i}$ and $P_{1i}$, respectively, computed under the constraint $\tilde{p}_{1i}=\tilde{p}_{0i}+S_0$.  


The p-value can be calculated as stated above.

# Paramters in Function
| Parameters | Description                | Default | 
|:-----------|:---------------------------|:---------|
|formula    |A symolic description of the model to be fitted, which has the form \code{response ~ treament}, where \code{response} is the numeric vector with values of 0 or 1 and \code{treatment} is the group information.   |       |
|data      |an optional data frame, list or environment containing the variables in the model. | |
|delta      |A numeric value to set the difference of two group under the null.|0       |
|weight_schema      |Weighting schema used in stratified MN method. "equal", "ss" and "cmh". |ss       |
|test      |A character string specifying the side of p-value, must be one of "right" (default), "left" or "two.sided".|right     |
|bisection      |The number of sections in the interval used in Bisection Method.|100       |
|eps      |The level of precision. |1e-06   |
|alpha      |Pre-difined alpha level for two-sided confidence interval.|0.05       |

# Load Function
```{r message=FALSE}
library(dplyr)
library(tidyr)
source("rate0compare.R",local = knitr::knit_global())
```

# Data Simulation
```{r}
treatment <- c(rep(0,100),rep(1,100))
response <- c(rep(0,80),rep(1,20),rep(0,40),rep(1,60))
stratum <- c(rep(1:4,12),1,3,3,1,rep(1:4,12),rep(1:4,25))
```

# Unstratified Analysis
The function computes the risk difference, Z-statistic, p-value given the type of test, and two-sided $100(1-\alpha)$% confidence interval of difference between two rates. 

```{r}
rate0compare(response~treatment,delta = 0, bisection= 100, eps=1e-06, test = "one.sided",alpha=0.05)
```

To compare with SAS standard macro results, the macro was run on the same dataset with the unstratified MN method. The estimated risk difference and confidence interval are on percentile level from SAS output:
```{r message=FALSE,echo=FALSE} 
library(SASmarkdown)
saspath <- "C:/Program Files/SASHome/x86/SASFoundation/9.4/sas.exe"
sasopts <- "-nosplash -linesize 75"
knitr::opts_chunk$set(engine="sashtml", engine.path=saspath, 
        engine.opts=sasopts, comment=NA)
```
```{r,collectcode=TRUE,echo=FALSE}
%include "\\bardsar-test\mk7902-nsclc\prot008-ia1\adhoc\sample\pgm\dsvar.sas";
%include "\\bardsar-test\mk7902-nsclc\prot008-ia1\adhoc\sample\pgm\varattr.sas";
%include "\\bardsar-test\mk7902-nsclc\prot008-ia1\adhoc\sample\pgm\rate0compare.sas";
```

```{r}
data inds;
  input stratum n1 s1 n2 s2 ;
cards;
1 100 60 100 20 
;
run;

%rate0compare(
     input_dataset  = inds
    ,Output_dataset = observed
    ,Output_dataset2= adjusted
    ,Stratum_var    = stratum
    ,No_treatment   = 2
    ,By_var         = 
    ,Method         = MN
    ,Continuity_corr= 0
    ,Delta          = 0
    ,Weight_schm    = 5
    ,Ci             = 95
    ,Exposure_adj   = 0
    ,Testing        = 1
    ,Debug          = N
);

proc print data=adjusted;
var trtdiff z_diff l_bound u_bound p_value;
run;
```


# Stratified Analysis
The sample size weighting is often used in the clinical trial. Below is the function to conduct stratified MN analysis with sample size weights.
```{r,engine='R'}
rate0compare(formula=response~treatment+strata(stratum),
                         delta = 0, weight_schema="ss",bisection= 100, eps=1e-06,
                         test = "one.sided",alpha=0.05)
```
To compare with SAS standard macro results, the macro was run on the same dataset with the stratified MN method using sample size as weights. The estimated risk difference and confidence interval are on percentile level from SAS output:

```{r,engine="sashtml",collectcode=TRUE}
data inds;
  input stratum n1 s1 n2 s2 ;
cards;
1 25 15 26 5 
2  25 15 24 5
3 25 15 26 5 
4  25 15 24 5
;
run;

%rate0compare(
     input_dataset  = inds
    ,Output_dataset = observed
    ,Output_dataset2= adjusted
    ,Stratum_var    = stratum
    ,No_treatment   = 2
    ,By_var         = 
    ,Method         = MN
    ,Continuity_corr= 0
    ,Delta          = 0
    ,Weight_schm    = 2
    ,Ci             = 95
    ,Exposure_adj   = 0
    ,Testing        = 1
    ,Debug          = N
);

proc print data=adjusted;
var trtdiff z_diff l_bound u_bound p_value;
run;
```

